Through the eyes of the teacher

### 2021-02-09 paper_1/paper_1_supplement.Rmd
update GRI

```
\newpage
Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment. The following graph shows the duration of speaking time for experts and novices evaluated by the observer, the students and the teacher.

```{r Duration speaking time, fig.width=5, fig.height = 5, echo = FALSE}
# prepare data (selected from questionnaire data)
quest.raw.data<-read.table("./data/short_questionnaire_data_2701211.txt", dec=",", sep="\t", header=T)

# to compare both sessions filter only Identical items
quest.raw.data <- quest.raw.data  %>% filter(str_detect(scale, 
                                                 paste(c("Duration of speaking time"),
                                                    collapse = '|')))
view(quest.raw.data)

quest.raw.data <- quest.raw.data %>% mutate (speaking.data)

speaking.plot <- quest.raw.data %>%
  ggplot(aes(x='Duration of speaking time', y=value, fill=group)) +
    geom_boxplot() +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme_light() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11),
      axis.text.x = element_text(size = 8)) +
    facet_grid(group~perspective) +
    ggtitle("Boxplot with individual points for Duration of speaking time") +
    xlab("")
speaking.plot

@@

# prepare data (selected from questionnaire data)
et.raw.data<-read.table("./data/Aperol_pilot_glasses_AOI.tsv", dec=",", sep="\t", header=T)

# converting integer to numeric
et.raw.data <- et.raw.data %>%  mutate(Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations))

@@

# create a basic table (tibble) using tidyverse functions
et.raw.table <- et.raw.data %>%
  group_by(Participant, Variable) %>%
  summarise("Fixation Number" = Number_of_whole_fixations,
            "Average Duration Fixation" = Average_duration_of_whole_fixations,
            "SE Duration Fixation" = se(Total_duration_of_whole_fixations),
            "TOI length" = TOI,
            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)

view(et.raw.table)

# format and insert table in manuscript
apa_table(
  et.raw.table,
  caption = "Number and Duration (in msec) of Fixations",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

@@

```{r boxplot GRI, fig.width=6, fig.height = 8, echo = FALSE}

et.plot <- et.raw.data %>%
  ggplot(aes(x=Number_of_whole_fixations, y=value, fill=scale)) +
    geom_boxplot() +
    scale_x_discrete(guide = guide_axis(angle = 70)) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    theme_light() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    facet_grid(~Variable)+
    ggtitle("Boxplot with individual points for Number of fixations") +
    xlab("")
et.plot

>>>>

@@

# prepare data (selected from questionnaire data)
et.data<-read.table("./data/Aperol_pilot_glasses_AOI.txt", dec=",", sep="\t", header=T)

view(et.data)
str(et.data)

# converting integer to numeric
et.data <- et.data %>%  mutate(Number.of.fixations.in.AOI = as.numeric(Number.of.fixations.in.AOI))

@@

# create a basic table (tibble) using tidyverse functions
et.table <- et.data %>%
  group_by(PersonID, Group) %>%
  summarise("Fixation Number" = Number.of.fixations.in.AOI,
            "Fixation Duration" = Total.duration.of.fixation.in.AOI..msec.,
            "Average Duration Fixation" = Average.duration.of.fixation.in.AOI..msec.,
            "SE Duration Fixation" = se(Total.duration.of.fixation.in.AOI..msec.),
            "TOI" = Total.Time.of.Interest.Duration..msec.,
            "GRI" = Average.duration.of.fixation.in.AOI..msec. / Number.of.fixations.in.AOI)

view(et.table)

# format and insert table in manuscript
apa_table(
  et.table,
  caption = "Number and Duration (in msec) of Fixations",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

@@

```{r boxplot GRI, fig.width=6, fig.height = 8, echo = FALSE}
# 
# et.plot <- et.raw.data %>%
#   ggplot(aes(x=Number_of_whole_fixations, y=value, fill=scale)) +
#     geom_boxplot() +
#     scale_x_discrete(guide = guide_axis(angle = 70)) +
#     geom_jitter(color="black", size=0.4, alpha=0.9) +
#     theme_light() +
#     theme(
#       legend.position="none",
#       plot.title = element_text(size=11)
#     ) +
#     facet_grid(~Variable)+
#     ggtitle("Boxplot with individual points for Number of fixations") +
#     xlab("")
# et.plot
